### 2017-05-05 paper/evaluation.tex
added vertical line for readability
preliminar values from RQ6

\begin{figure*}[t]
\centering
\small
\begin{tabular}{lccccccccccc}
\toprule
\multirow{2}{*}{\emph{Subject}} & \emph{\Seq{}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T_\text{cost}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
Choco Solver & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%

>>>>

\begin{figure*}[t]
\centering
\small
\begin{tabular}{l|c|cccccccccc}
\toprule
\multirow{2}{*}{\emph{Subject (module)}} & \emph{\Seq{}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T_\text{cost}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
    OpenMRS Core (\CodeIn{api})           & 13.8m & \entry{1.04}{58.07} & \entry{1.86}{65.55} & \entry{2.01}{61.56} & \entry{1.51}{0} & \colheader{X}\\%
Apache Flume (\CodeIn{flume-ng-core}) & 8.3m & \entry{2.82}{18.11} & \entry{1.07}{0} & \entry{2.78}{16.84} & \entry{0.98}{0} & \entry{2.87}{18.88}\\%
Apache Giraph (\CodeIn{giraph-core})  & 7m & \entry{2.08}{5.08} & \colheader{X} & \entry{1.01}{0} & \entry{1}{B} & \colheader{X}\\%
